
``` {r echo=FALSE, results="asis"}
## Nothing to see here ... move along
require("questionr", quietly=TRUE)
page <- questionr:::Page$new()
nav <- questionr:::NavBar$new()
cat(page$write_header())
```


`r I(nav$write_header("The Kitchen Sink Example", "Shows off different elements of this R package"))`

`r I(nav$add("About"))`

This `R` package provides a simple enough means to write quizzes or
homework-type assignments to be displayed on the web using the easy to
learn `R markdown` format. This format makes integrating formatted
text, `R` code, and `R` graphics as simple as possible.  A number of R
functions are given to make the pages quiz-ready.  The `Twitter
Bootstrap` CSS and JavaScript files are used for styling the pages, to
given an attractive, modern look with _minimal_ fuss from the author.

`r I(nav$add("Markup"))`

The basic format for authoring is `R markdown`, This format that can
be easily used from within `RStudio` -- where there is a very nice
mode for interacting with such documents. However, it can also be
authored with any text editor and processed from any `R` session using
the `knitr` and `markdown` packages from CRAN.


There are few function calls from this package that are incorporated
to make an interactive page.

The main one is to create a new reference class instance (`page`
below) via a call:

    ```{r echo=FALSE, results="asis"}
    page <- questionr:::Page$new()
    nav <- questionr:::NavBar$new()
    cat(page$write_header())
    cat(nav$write_header())
    ```


As seen, this is wrapped inside an R block with `echo=FALSE,
results="asis"` specified.



(An R block is a triple backtick block with the `{r}` bit added. We
also use inline R calls. For blocks, the "asis" is important as the function return a mix of HTML and JavaScript. For inline code, one must wrap the function within an `I()` to avoid the processing of the text into HTML readable format.)

The navigation bit is optional, but adds quite a bit for no real cost.

New problems are created using inline notation with various problem calls, as with

<code></pre>
&#96;r I(page$radio_choice(x, value, hint, ...))&#96;
</pre></code>

There are other problem types, the above syntax will produce an HTML
snippet to offer the user a selection from a list of items using radio
buttons.

The page is finished by selecting a button for grading (locally, or
with a server) and closing the (optional) navigation tags and writing
the footer for the page:

    ```{r echo=FALSE, results=TRUE}   
    cat(nav$write_footer())
    cat(grade_button())
    cat(page$write_footer())
    ```



`r I(nav$add("Navigation"))`

At the top of the page, the black navigation bar and its links are for
navigation. They come from the methods `write_header`, `add`, and
`write_footer` of a `NavBar` object. The `add` method simply places an
anchor in the file and adds a menu item to the navigation bar. By
default, it will also write a section header to the file, though this
can be suppressed.



`r I(nav$add("Problem types", "Types of problems that we can do"))`

These are the main problem types:

`r I(label("Numeric choice"))` A `numeric_choice` allows the user to
enter a number. One specifies an upper and lower bound on acceptable
numbers:

`r I(page$numeric_choice(exp(1), pi,  comment=list(less="A little low", more="A little high"),hint="Between e and pi"))`

`r I(label("Radio choice"))` A `radio_choice` offers the user radio
buttons to select a value from:

`r I(page$radio_choice(state.name[1:4], state.name[1], comment=list("Alaska"="I can see Russia from there, but it is not the right answer."), hint="first one"))`


`r I(label("Checkbox group choice"))` A `checkgroup_choice` is
similar, though a user can select one or more answer

`r I(page$checkgroup_choice(state.name[1:4], state.name[1], hint="first one"))`


`r I(label("Combobox choice"))` A `combobox_choice` is similar to the
radio, though allows for many more choices in a more compact manner:

`r I(page$combobox_choice(state.name, state.name[1], hint="first one"))`

`r I(label("Typeahead choice"))` A `typeahead_choice` is similar to
the combobox, but the items to choose from aren't shown initially, but
rather only in narrowed form after the user has started typing.


`r I(page$typeahead_choice(state.name, state.name[1], hint="Sweet home ..."))`

Problems can include hints and problems can have comments specified
for predictable mistakes. The `hint` and `comment` arguments are used for these.


`r I(nav$add("Other markup", "some extra features provided by Bootstrap"))`

We use the wonderful `Bootstrap` CSS and JavaScript libraries provided
by twitter (http://twitter.github.com/bootstrap/index.html). These
libraries provide many great classes for styling a page and some
JavaScript libraries for adding dynamic features. One can incorporate
raw HTML within a `R markdown` page and this markup can include the
classes provided by `Bootstrap`. This allows one to use the libraries
directly.

`r I(alert("Warning", "The markdown package uses the sundown package for converting markdown format to HTML. This conversion handles the embedded R code within block-level tags (e.g. a 'div' tag) in such a way that the R code is not displayed as desired. Sometimes, wrapping within a 'span' tag will prevent this."))`

This `R` package provides a few convenience functions to access a
sliver of the Bootstrap functionality:

<h3>Tabs</h3>

By default, the components are all laid out vertically, making for
long pages. Using tabs we can break this up by only disclosing parts
of the page that a user requests through clicking on a tab. 

There can be more than one tabbed area per page, so we need to create
a separate `Tabs` instance for each and then add to the page. The main methods are
`write_header`, `write_footer`, and `add`. The first two wrap the
content to be placed in the tabs, the latter creates the pages.

A basic structure looks like

    ```{r echo=FALSE, results="asis"}
    tabs <- questionr:::Tabs$new()
    cat(tabs$write_header())
    ```

Then to add a tab, we have

<code><pre>
&#96;r I(tabs$add("New tab"))&#96;
</pre></code>

And after finishing specifying the tabs, one writes a footer:
    
<code><pre>
&#96;r I(tabs$write_footer())&#96;
</pre></code>

In this example we use tabs to show a linear model and a diagnostic
plot.

```{r echo=FALSE,results="asis"}
tabs <- questionr:::Tabs$new()
cat(tabs$write_header())
```

`r I(tabs$add("The model"))`

```{r}
res <- lm(mpg ~ wt, mtcars)
summary(res)
```

`r I(tabs$add("Diagnostic plot"))`

```{r}
plot(res, which=1)
```

`r I(tabs$write_footer())`


<h3>Some markup</h3>

There are various conveniences to access `Bootstrap`'s excellent CSS
styling. One can make labels with `label`: `r I(label("some warning
label", type="warning"))`.

<br />

A "badge" is somewhat familiar to Apple users. The `badge` function does so: `r I(badge("pi", type="warning"))`.

<br />

Alerts are dismissible areas to display a message. They are made with
the `alert` function.

`r I(alert("Whoa Nelly!", "This is some alert message"))`


`r I(nav$add("Graphics"))`

Inserting graphics into a document is dead simple with `R
markdown`. The `knitr` package handles the production of the graphics,
and `markdown` embed the graphic directly into the HTML file so there
is no fuss with hosting of graphics.

```{r echo=FALSE, results="asis"}
tabs <- questionr:::Tabs$new()
cat(tabs$write_header())
cat(tabs$add("Basic"))
```

    ``` {r}
    ## a basic graphic is just done within the triple-backtick block:
    hist(rnorm(100))
    ```

```{r echo=FALSE}
hist(rnorm(100))
```

`r I(tabs$add("Google graphics"))`

The `googleVis` package integrates R with Google's visualization
API. As with the basic graphics, all the necessary code to display the
graph is contained in the one HTML file, making it easy to
upload/mail/host these pages.

```{r results="asis"}
suppressPackageStartupMessages(library(googleVis))
T <- gvisTable(Exports, options = list(width = 200, height = 280))
G <- gvisGeoChart(Exports, locationvar = "Country", colorvar = "Profit", 
    options = list(width = 360, height = 280, dataMode = "regions"))
TG <- gvisMerge(T, G, horizontal = TRUE, tableOptions = "bgcolor=\"#CCCCCC\" cellspacing=10")

print(TG, "chart")
```



`r I(tabs$write_footer())`


<!--- Finish this off -->

`r I(nav$write_footer())`

`r I(page$grade_button())`

`r I(page$write_footer())`
